Relationships in the extremes and their influence on competition and coexistence

### 2022-02-16 paper/Paper.Rnw
some edits to results

%G4
Fulfilling goal G4 of the Introduction (to provide an empirical example of species coexistence which highlights the role ATAs can play), Fig. \ref{fig:fig5} and Fig. \ref{fig:fig6} 
show that the ATA contributions have magnitudes comparable to the 
magnitudes of other terms of the extended MCT decomposition and 
parameters subspaces exist where ATA rescue occurs. 
Fig.\ref{fig:fig5} plots the importance of various coexistence mechanisms for the 
persistence of \emph{F. crotonensis} and they're sum, the IGR
(see eq. \ref{eq:full_decomp}), for different varying temperature parameters 
($a$, $P$, and $\theta_0$) with two of the three parameters set constant in each plot.
Increasing amplitude and mean temperature showed increasing trends in the IGR and 
decomposed coexistence mechanisms, while increasing periodicity showed less change. 
Within the investigated parameters of Fig.\ref{fig:fig5}, ATA contribution, $\Delta_i^{[EC]}$, 
is always positive, even in cases where IGR is negative, and is almost always second to 
the contribution of varying environment, $\Delta_i^{E}$, 
including for the temperature parameters which \emph{F. crotonensis} 
and \emph{C. pseudostelligera} coexisted \emph{in vitro} ? \cite{Descamps_2005}.  
ATA rescue is revealed in Fig.\ref{fig:fig5} within parameter subspaces where the absence of 
ATA contribution would lead to exclusion of \emph{F. crotonensis}.
IGR decomposition of \emph{C. psuedostelligera} across the same subsets of
temperature parameters revealed that its IGR is always positive and the ATA contribution is 
not meaningful (see SI section). %Mean EC shows a rescue effect against variance in E

@@

>>>>

%G4
Fulfilling goal G4 of the Introduction (to provide an empirical example of species coexistence which highlights the role ATAs can play), Fig. \ref{fig:fig5} and Fig. \ref{fig:fig6} 
show that the ATA contributions have magnitudes comparable to the 
magnitudes of other terms of the extended MCT decomposition and 
parameters subspaces exist where ATA rescue occurs. 
Fig.\ref{fig:fig5} plots the importance of various coexistence mechanisms for the 
persistence of \emph{F. crotonensis} and they're sum, the IGR
(see eq. \ref{eq:full_decomp}), for different varying temperature parameters 
($a$, $P$, and $\theta_0$) with two of the three parameters set constant in each plot.
Increasing amplitude and mean temperature showed increasing trends in the IGR and 
decomposed coexistence mechanisms, while increasing periodicity showed less change. 
Within the investigated parameters of Fig.\ref{fig:fig5}, ATA contribution, $\Delta_i^{[EC]}$, 
is always positive, even in cases where IGR is negative, and is almost always second to 
the contribution of varying environment, $\Delta_i^{E}$, 
including for the temperature parameters which \emph{F. crotonensis} 
and \emph{C. pseudostelligera} coexisted \emph{in vitro} ? \cite{Descamps_2005}.  
ATA rescue is revealed in Fig.\ref{fig:fig5} within parameter subspaces where the absence of 
ATA contribution would lead to exclusion of \emph{F. crotonensis}.

@@

IGR decomposition of \emph{C. psuedostelligera} across the same subsets of
temperature parameters revealed that its IGR is always positive; though, the ATA contribution is not meaningful to its persistence (see SI section). %Mean EC shows a rescue effect against variance in E
Thus, the coexistence of the two diatom species depends only on the persistance of 
\emph{F. crotonensis} and its ability to invade when rare. Additionally, because ATAs 
meaningfully contribute to the IGR of \emph{F. crotonensis}, ATAs then also contribute 
meaningfully to the coexistence of \emph{F. crotonensis} and \emph{C. psuedostelligera}.
